---
title: "Seedcoat Results"
author: "Kelsey McGurrin"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,include = TRUE,message = FALSE)

#### setup ####
#packages
library(tidyverse)
library(lme4)
library(lmerTest)


#### import insect data ####

insects<-read_csv("~/Dropbox/bean_dip_2018-2024/field trials/data/clean_data/clean_insects.csv") %>%
  filter(count > 0) %>% # only include insects found
  mutate(variety_name = case_when(year==2019 & variety %in% c(67,27) ~ "AG38X8",
                                  year==2020 & variety %in% c(2,5) ~ "AG38X8",
                                  year==2021 & variety %in% c(19,59) ~ "AG38X8",
                                  year==2019 & variety == 83 ~ "SH3814LL",
                                  year==2020 & variety == 50 ~ "SH3814LL",
                                  year==2021 & variety %in% c(57,58) ~ "SH3814LL")) %>% # add in brands
  rename(seed_coat=treatment_agg) %>%
  filter(variety_name=="AG38X8" & year== c(2019,2020,2021) 
         | variety_name=="SH3814LL" & year== 2021) # only varieties and years where we have both treated/untreated

# most functional groups too few to do stats
insects |> group_by(functional_group) |> summarize(sum=sum(count)) |> arrange(desc(sum))
target_insects <- insects %>%
  filter(functional_group %in% c("sucking","chewing","predator","pollinator")) # 80% of data anyway

# so sites display properly from west to east
target_insects$site<-factor(target_insects$site, levels = c("K", "C", "W", "PH"))


#### import damage data ####
damage2019 <- read.csv('~/Dropbox/bean_dip_2018-2024/field trials/data/clean_data/clean_damage_2019.csv') %>% 
  mutate(pct_pucker='NA', year=2019)
damage2020 <- read.csv('~/Dropbox/bean_dip_2018-2024/field trials/data/clean_data/clean_damage_2020.csv') %>% 
  mutate(pct_pucker='NA', year=2020)
damage2021 <- read.csv('~/Dropbox/bean_dip_2018-2024/field trials/data/clean_data/clean_damage_2021.csv') %>% 
  mutate(year=2021)
# damage2022 <- read.csv('clean_damage_2022.csv') %>% # don't include 2022 because we only have data for untreated
#   select(-...18, -plot_id) %>% 
#   mutate(pct_pucker='NA', year=2022) %>% 
#   rename(pct_damage_stippled=stip_pct)

damage <- rbind(damage2019, damage2020, damage2021) %>% #bind all data together
  # put in the real variety names and whether treated or untreated
  mutate(variety_name=ifelse(year==2019 & variety %in% c(67,27), 'AG38X8',
                             ifelse(year==2020 & variety %in% c(2,5), 'AG38X8',
                                    ifelse(year==2021 & variety %in% c(19,59), 'AG38X8',
                                           ifelse(year==2022 & variety %in% c(73), 'AG38X8',
          ifelse(year==2019 & variety==83, 'SH3814LL',
                 ifelse(year==2020 & variety==50, 'SH3814LL',
                        ifelse(year==2021 & variety %in% c(57,58), 'SH3814LL',
          ifelse(year==2019 & variety==31, 'S39-G2X',
                 ifelse(year==2020 & variety==70, 'S39-G2X',
                        ifelse(year==2021 & variety==82, 'S39-G2X',
          ifelse(year==2019 & variety==55, '7390ET',
          ifelse(year==2019 & variety==32, '539XT', 'NA'))))))))))))) %>% 
  mutate(seed_coat=ifelse(year==2019 & variety==67, 'untrt',
                          ifelse(year==2020 & variety==2, 'untrt',
                                 ifelse(year==2021 & variety %in% c(19,57), 'untrt',
                                        ifelse(year==2022 & variety==73, 'untrt', 'trt'))))) %>% 
  filter(variety_name=="AG38X8" & year== c(2019,2020,2021) # only varieties and years where we have both treated/untreated
         | variety_name=="SH3814LL" & year== 2021) %>%
  mutate(stip_pct=(pct_leaves_stippled*as.numeric(pct_damage_stippled))/100,.after=chew_pct,.keep="unused") %>% #calculate stippling
  select(-c(density,mammals,insects,insect.names,pct_pucker)) %>% # drop unnecessary columns
  group_by(year, sampling.round, site, variety_name, seed_coat, plot) %>% # average rows a and b to get one value per plot
  summarise(across(chew_pct:pct_yellow_leaf, ~ mean(.x, na.rm = TRUE))) %>%
  ungroup()

# so sites display properly from west to east
damage$site<-factor(damage$site, levels = c("K", "C", "W", "PH"))


#### import biomass data ####

# open clean data file 
# filter so only varieties/years where we have a treated/untreated comparison
biomass<-read_csv("~/Dropbox/bean_dip_2018-2024/field trials/data/clean_data/clean_all_years_long.csv") %>%
  filter(brandline=="AG38X8" & year== c(2019,2020,2021) 
         | brandline=="SH3814 LL" & year== 2021) %>%
  select(year:plot_yield_buac)

# so sites display properly from west to east
biomass$site<-factor(biomass$site, levels = c("K", "C", "W", "PH"))

```

# AG38X8 only

## Chewing Damage
```{r echo=FALSE}
# subset data for analysis
AG_damage<-damage %>%
  filter(variety_name=="AG38X8")

# summary table for graphs
AG_damage_siteAvgDf<-damage %>%
  filter(variety_name=="AG38X8") %>%
  group_by(sampling.round,site,year,seed_coat) %>%
  summarise(site_avg_chew=mean(chew_pct,na.rm=T),
            se_avg_chew=sd(chew_pct,na.rm = T)/sqrt(n()),
            site_avg_stip=mean(stip_pct,na.rm=T),
            se_avg_stip=sd(stip_pct,na.rm=T)/sqrt(n()))

# percent chew panels
ggplot(AG_damage_siteAvgDf, aes(x=sampling.round,y=site_avg_chew,colour=seed_coat,group=seed_coat))+
  facet_grid(rows=vars(year),cols=vars(site))+geom_point()+geom_line()+
  geom_errorbar(aes(ymin=site_avg_chew-se_avg_chew,
                    ymax=site_avg_chew+se_avg_chew),width=0.2)+
  labs(title="AG38X8",y="Avg % Chew ± SE")
```

```{r echo=TRUE}
AG_chew_mod<-lmer(chew_pct~year*sampling.round*seed_coat+(1|site/variety_name),data=AG_damage)

anova(AG_chew_mod)
summary(AG_chew_mod)
plot(AG_chew_mod)
hist(residuals(AG_chew_mod))
```


## Stippling Damage
```{r echo=FALSE}
# percent stippling panels
ggplot(AG_damage_siteAvgDf, aes(x=sampling.round,y=site_avg_stip,colour=seed_coat,group=seed_coat))+
  facet_grid(rows=vars(year),cols=vars(site))+geom_point()+geom_line()+
  geom_errorbar(aes(ymin=site_avg_stip-se_avg_stip,
                    ymax=site_avg_stip+se_avg_stip),width=0.2)+
  labs(title="AG38X8",y="Avg % Stippling ± SE")
```

```{r echo=TRUE}
AG_stip_mod<-lmer(stip_pct~year*sampling.round*seed_coat+(1|site/variety_name),data=AG_damage)

anova(AG_stip_mod)
summary(AG_stip_mod)
plot(AG_stip_mod)
hist(residuals(AG_stip_mod))
```



## Chewing Insects
```{r echo=FALSE}
# subset data for analysis
AG_insects <- target_insects %>%
  filter(variety_name == "AG38X8")

# summary table for graphs
AG_chewer_siteAvgDf<-target_insects %>%
  filter(variety_name=="AG38X8" & functional_group == "chewing") %>%
  group_by(sampling_round,site,year,seed_coat) %>%
  summarise(site_avg_chewers=mean(count,na.rm=T),
            se_avg_chewers=sd(count,na.rm = T)/sqrt(n()))

# count chewers panels
ggplot(AG_chewer_siteAvgDf, aes(x=sampling_round,y=site_avg_chewers,colour=seed_coat,group=seed_coat))+
  facet_grid(rows=vars(year),cols=vars(site))+geom_point()+geom_line()+
  geom_errorbar(aes(ymin=site_avg_chewers-se_avg_chewers,
                    ymax=site_avg_chewers+se_avg_chewers),width=0.2)+
  labs(title="AG38X8",y="Avg # Chewing Insects ± SE")  

```
```{r echo=TRUE}
AG_chewer_mod<-lmer(count~year*sampling_round*seed_coat+(1|site/variety_name),
                    data=AG_insects %>% filter(functional_group=="chewing"))

hist(AG_insects$count[AG_insects$functional_group=="chewing"])

anova(AG_chewer_mod)
summary(AG_chewer_mod)
plot(AG_chewer_mod)
hist(residuals(AG_chewer_mod))
```


## Sucking Insects
```{r echo=FALSE}

# summary table for graphs
AG_sucker_siteAvgDf<-target_insects %>%
  filter(variety_name=="AG38X8" & functional_group == "sucking") %>%
  group_by(sampling_round,site,year,seed_coat) %>%
  summarise(site_avg_suckers=mean(count,na.rm=T),
            se_avg_suckers=sd(count,na.rm = T)/sqrt(n()))

# count suckers panels
ggplot(AG_sucker_siteAvgDf, aes(x=sampling_round,y=site_avg_suckers,colour=seed_coat,group=seed_coat))+
  facet_grid(rows=vars(year),cols=vars(site))+geom_point()+geom_line()+
  geom_errorbar(aes(ymin=site_avg_suckers-se_avg_suckers,
                    ymax=site_avg_suckers+se_avg_suckers),width=0.2)+
  labs(title="AG38X8",y="Avg # Sucking Insects ± SE")  

```
```{r echo=TRUE}
AG_sucker_mod<-lmer(count~year*sampling_round*seed_coat+(1|site/variety_name),
                    data=AG_insects %>% filter(functional_group=="sucking"))

anova(AG_sucker_mod)
summary(AG_sucker_mod)
plot(AG_sucker_mod)
hist(residuals(AG_sucker_mod))
```

## Herbivores
Chewing AND sucking insects together
```{r echo=FALSE}

# summary table for graphs
AG_herb_siteAvgDf<-target_insects %>%
  filter(variety_name=="AG38X8" & functional_group %in% c("chewing","sucking")) %>%
  group_by(sampling_round,site,year,seed_coat) %>%
  summarise(site_avg_herb=mean(count,na.rm=T),
            se_avg_herb=sd(count,na.rm = T)/sqrt(n()))

# count herbivores panels
ggplot(AG_herb_siteAvgDf, aes(x=sampling_round,y=site_avg_herb,colour=seed_coat,group=seed_coat))+
  facet_grid(rows=vars(year),cols=vars(site))+geom_point()+geom_line()+
  geom_errorbar(aes(ymin=site_avg_herb-se_avg_herb,
                    ymax=site_avg_herb+se_avg_herb),width=0.2)+
  labs(title="AG38X8",y="Avg # Herbivores ± SE")  

```
```{r echo=TRUE}
AG_herb_mod<-lmer(count~year*sampling_round*seed_coat+(1|site/variety_name),
                    data=AG_insects %>% filter(functional_group%in% c("chewing","sucking")))

anova(AG_herb_mod)
summary(AG_herb_mod)
plot(AG_herb_mod)
hist(residuals(AG_herb_mod))
```

## Predators
```{r echo=FALSE}

# summary table for graphs
AG_pred_siteAvgDf<-target_insects %>%
  filter(variety_name=="AG38X8" & functional_group == "predator") %>%
  group_by(sampling_round,site,year,seed_coat) %>%
  summarise(site_avg_pred=mean(count,na.rm=T),
            se_avg_pred=sd(count,na.rm = T)/sqrt(n()))

# count predators panels
ggplot(AG_pred_siteAvgDf, aes(x=sampling_round,y=site_avg_pred,colour=seed_coat,group=seed_coat))+
  facet_grid(rows=vars(year),cols=vars(site))+geom_point()+geom_line()+
  geom_errorbar(aes(ymin=site_avg_pred-se_avg_pred,
                    ymax=site_avg_pred+se_avg_pred),width=0.2)+
  labs(title="AG38X8",y="Avg # Predators ± SE")  

```
```{r echo=TRUE}
AG_pred_mod<-lmer(count~year*sampling_round*seed_coat+(1|site/variety_name),
                    data=AG_insects %>% filter(functional_group=="predator"))

anova(AG_pred_mod)
summary(AG_pred_mod)
plot(AG_pred_mod)
hist(residuals(AG_pred_mod))
```



## Pollinators
```{r echo=FALSE}

# summary table for graphs
AG_poll_siteAvgDf<-target_insects %>%
  filter(variety_name=="AG38X8" & functional_group == "pollinator") %>%
  group_by(sampling_round,site,year,seed_coat) %>%
  summarise(site_avg_poll=mean(count,na.rm=T),
            se_avg_poll=sd(count,na.rm = T)/sqrt(n()))

# count pollinators panels
ggplot(AG_poll_siteAvgDf, aes(x=sampling_round,y=site_avg_poll,colour=seed_coat,group=seed_coat))+
  facet_grid(rows=vars(year),cols=vars(site))+geom_point()+geom_line()+
  geom_errorbar(aes(ymin=site_avg_poll-se_avg_poll,
                    ymax=site_avg_poll+se_avg_poll),width=0.2)+
  labs(title="AG38X8",y="Avg # Pollinators ± SE")  

```
```{r echo=TRUE}
AG_poll_mod<-lmer(count~year*sampling_round*seed_coat+(1|site/variety_name),
                    data=AG_insects %>% filter(functional_group=="pollinator"))

anova(AG_poll_mod)
summary(AG_poll_mod)
plot(AG_poll_mod)
hist(residuals(AG_poll_mod))
```


## Plant Biomass
```{r echo=FALSE}
# subset data for analysis
AG_biomass<-biomass %>%
  filter(brandline=="AG38X8")

# summary table for graphs
AG_biomass_siteAvgDf<-biomass %>%
  filter(brandline=="AG38X8") %>%
  group_by(site,year,brandline,seed_treat) %>%
  summarise(site_avg_plant_biomass=mean(plant_biomass_g,na.rm=T),
            se_plant_biomass=sd(plant_biomass_g,na.rm = T)/sqrt(n()),
            site_avg_beans=mean(beans_g,na.rm=T),
            se_beans=sd(beans_g,na.rm = T)/sqrt(n()),
            site_avg_yield=mean(plot_yield_buac,na.rm=T),
            se_yield=sd(plot_yield_buac,na.rm = T)/sqrt(n()))

# plant biomass panels
ggplot(AG_biomass_siteAvgDf,aes(x=site,y=site_avg_plant_biomass,group=seed_treat,color=seed_treat))+
         geom_line(size=1.5)+
         geom_point()+
         geom_errorbar(aes(ymin=site_avg_plant_biomass-se_plant_biomass,
                           ymax=site_avg_plant_biomass+se_plant_biomass),width=0.2,size=1.5)+
         facet_wrap(~year,nrow=1)+
  labs(title="AG38X8",y="Avg Whole Plant Biomass (g) ± SE")
```

```{r echo=TRUE}
AG_biomass_mod<-lmer(plant_biomass_g~year*seed_treat+(1|site/brandline),data=AG_biomass)

anova(AG_biomass_mod)
summary(AG_biomass_mod)
plot(AG_biomass_mod)
hist(residuals(AG_biomass_mod))
```

## Trial Yield
```{r echo=FALSE}
# trial yield panels
ggplot(AG_biomass_siteAvgDf,aes(x=site,y=site_avg_yield,group=seed_treat,color=seed_treat))+
         geom_line(size=1.5)+
         geom_point()+
         geom_errorbar(aes(ymin=site_avg_yield-se_yield,
                           ymax=site_avg_yield+se_yield),width=0.2,size=1.5)+
         facet_wrap(~year,nrow=1)+
  labs(title="AG38X8",y="Avg Plot Yield (bu/ac) +/- SE")
```

```{r echo=TRUE}
AG_yield_mod<-lmer(plot_yield_buac~year*seed_treat+(1|site/brandline),data=AG_biomass)

anova(AG_yield_mod)
summary(AG_yield_mod)
plot(AG_yield_mod)
hist(residuals(AG_yield_mod))
```




# SH3814LL only
Note: Keedysville herbicide damage - skipped survey sampling.round 3, round 4 only measured surviving stalks. Mean density went from ~ 16 stems to ~ 6 stems

## Chewing Damage
```{r  echo=FALSE}
# subset data for analysis
SH_damage<-damage %>%
  filter(variety_name=="SH3814LL")

# summary table for graphs
SH_siteAvgDf<-damage %>%
  filter(variety_name=="SH3814LL") %>%
  group_by(sampling.round,site,seed_coat) %>%
  summarise(site_avg_chew=mean(chew_pct,na.rm=T),
            se_avg_chew=sd(chew_pct,na.rm = T)/sqrt(n()),
            site_avg_stip=mean(stip_pct,na.rm=T),
            se_avg_stip=sd(stip_pct,na.rm=T)/sqrt(n()))

# percent chew panels
ggplot(SH_siteAvgDf, aes(x=sampling.round,y=site_avg_chew,colour=seed_coat,group=seed_coat))+
  facet_wrap(~site,nrow=1)+geom_point()+geom_line()+
  geom_errorbar(aes(ymin=site_avg_chew-se_avg_chew,
                    ymax=site_avg_chew+se_avg_chew),width=0.2)+
  labs(title="SH3814LL",y="Avg % Chew ± SE")
```

```{r echo=TRUE}
SH_chew_mod<-lmer(chew_pct~year*sampling.round*seed_coat+(1|site/variety_name),data=SH_damage)

anova(SH_chew_mod)
summary(SH_chew_mod)
plot(SH_chew_mod)
hist(residuals(SH_chew_mod))
```

## Stippling Damage
```{r echo=FALSE}
# percent stippling panels
ggplot(SH_siteAvgDf, aes(x=sampling.round,y=site_avg_stip,colour=seed_coat,group=seed_coat))+
  facet_wrap(~site,nrow=1)+geom_point()+geom_line()+
  geom_errorbar(aes(ymin=site_avg_stip-se_avg_stip,
                    ymax=site_avg_stip+se_avg_stip),width=0.2)+
  labs(title="SH3814LL",y="Avg % Stippling ± SE")
```

```{r echo=TRUE}
SH_stip_mod<-lmer(stip_pct~year*sampling.round*seed_coat+(1|site/variety_name),data=SH_damage)

anova(SH_stip_mod)
summary(SH_stip_mod)
plot(SH_stip_mod)
hist(residuals(SH_stip_mod))
```


## Chewing Insects
```{r echo=FALSE}
# subset data for analysis
SH_insects <- target_insects %>%
  filter(variety_name == "SH3814LL")

# summary table for graphs
SH_chewer_siteAvgDf<-target_insects %>%
  filter(variety_name=="SH3814LL" & functional_group == "chewing") %>%
  group_by(sampling_round,site,year,seed_coat) %>%
  summarise(site_avg_chewers=mean(count,na.rm=T),
            se_avg_chewers=sd(count,na.rm = T)/sqrt(n()))

# count chewers panels
ggplot(SH_chewer_siteAvgDf, aes(x=sampling_round,y=site_avg_chewers,colour=seed_coat,group=seed_coat))+
  facet_grid(rows=vars(year),cols=vars(site))+geom_point()+geom_line()+
  geom_errorbar(aes(ymin=site_avg_chewers-se_avg_chewers,
                    ymax=site_avg_chewers+se_avg_chewers),width=0.2)+
  labs(title="SH3814LL",y="Avg # Chewing Insects ± SE")  

```
Note: angry model. Drop year because only 2021? Can variety be in any of these models since I'm filtering?
```{r echo=TRUE}
SH_chewer_mod<-lmer(count~year*sampling_round*seed_coat+(1|site/variety_name),
                    data=SH_insects %>% filter(functional_group=="chewing"))

SH_chewer_mod<-lmer(count~sampling_round*seed_coat+(1|site/variety_name),
                    data=SH_insects %>% filter(functional_group=="chewing"))

hist(SH_insects$count[SH_insects$functional_group=="chewing"])

# anova(SH_chewer_mod)
# summary(SH_chewer_mod)
# plot(SH_chewer_mod)
# hist(residuals(SH_chewer_mod))
```


## Sucking Insects
```{r echo=FALSE}

# summary table for graphs
SH_sucker_siteAvgDf<-target_insects %>%
  filter(variety_name=="SH3814LL" & functional_group == "sucking") %>%
  group_by(sampling_round,site,year,seed_coat) %>%
  summarise(site_avg_suckers=mean(count,na.rm=T),
            se_avg_suckers=sd(count,na.rm = T)/sqrt(n()))

# count suckers panels
ggplot(SH_sucker_siteAvgDf, aes(x=sampling_round,y=site_avg_suckers,colour=seed_coat,group=seed_coat))+
  facet_grid(rows=vars(year),cols=vars(site))+geom_point()+geom_line()+
  geom_errorbar(aes(ymin=site_avg_suckers-se_avg_suckers,
                    ymax=site_avg_suckers+se_avg_suckers),width=0.2)+
  labs(title="SH3814LL",y="Avg # Sucking Insects ± SE")  

```

Note: drop year here too? Why wasn't this a problem with damage and biomass models?
```{r echo=TRUE}
SH_sucker_mod<-lmer(count~year*sampling_round*seed_coat+(1|site/variety_name),
                    data=SH_insects %>% filter(functional_group=="sucking"))

anova(SH_sucker_mod)
summary(SH_sucker_mod)
plot(SH_sucker_mod)
hist(residuals(SH_sucker_mod))
```

## Herbivores
Chewing AND sucking insects together
```{r echo=FALSE}

# summary table for graphs
SH_herb_siteAvgDf<-target_insects %>%
  filter(variety_name=="SH3814LL" & functional_group %in% c("chewing","sucking")) %>%
  group_by(sampling_round,site,year,seed_coat) %>%
  summarise(site_avg_herb=mean(count,na.rm=T),
            se_avg_herb=sd(count,na.rm = T)/sqrt(n()))

# count herbivores panels
ggplot(SH_herb_siteAvgDf, aes(x=sampling_round,y=site_avg_herb,colour=seed_coat,group=seed_coat))+
  facet_grid(rows=vars(year),cols=vars(site))+geom_point()+geom_line()+
  geom_errorbar(aes(ymin=site_avg_herb-se_avg_herb,
                    ymax=site_avg_herb+se_avg_herb),width=0.2)+
  labs(title="SH3814LL",y="Avg # Herbivores ± SE")  

```
Note: drop year here too? Why wasn't this a problem with damage and biomass models?
```{r echo=TRUE}
SH_herb_mod<-lmer(count~year*sampling_round*seed_coat+(1|site/variety_name),
                    data=SH_insects %>% filter(functional_group%in% c("chewing","sucking")))

anova(SH_herb_mod)
summary(SH_herb_mod)
plot(SH_herb_mod)
hist(residuals(SH_herb_mod))
```

## Predators
```{r echo=FALSE}

# summary table for graphs
SH_pred_siteAvgDf<-target_insects %>%
  filter(variety_name=="SH3814LL" & functional_group == "predator") %>%
  group_by(sampling_round,site,year,seed_coat) %>%
  summarise(site_avg_pred=mean(count,na.rm=T),
            se_avg_pred=sd(count,na.rm = T)/sqrt(n()))

# count predators panels
ggplot(SH_pred_siteAvgDf, aes(x=sampling_round,y=site_avg_pred,colour=seed_coat,group=seed_coat))+
  facet_grid(rows=vars(year),cols=vars(site))+geom_point()+geom_line()+
  geom_errorbar(aes(ymin=site_avg_pred-se_avg_pred,
                    ymax=site_avg_pred+se_avg_pred),width=0.2)+
  labs(title="SH3814LL",y="Avg # Predators ± SE")  

```
Note: angry model
```{r echo=TRUE}
SH_pred_mod<-lmer(count~year*sampling_round*seed_coat+(1|site/variety_name),
                    data=SH_insects %>% filter(functional_group=="predator"))

# anova(SH_pred_mod)
# summary(SH_pred_mod)
# plot(SH_pred_mod)
# hist(residuals(SH_pred_mod))
```



## Pollinators
NOte: only 13 insects observed
```{r echo=FALSE}

# summary table for graphs
SH_poll_siteAvgDf<-target_insects %>%
  filter(variety_name=="SH3814LL" & functional_group == "pollinator") %>%
  group_by(sampling_round,site,year,seed_coat) %>%
  summarise(site_avg_poll=mean(count,na.rm=T),
            se_avg_poll=sd(count,na.rm = T)/sqrt(n()))

# count pollinators panels
ggplot(SH_poll_siteAvgDf, aes(x=sampling_round,y=site_avg_poll,colour=seed_coat,group=seed_coat))+
  facet_grid(rows=vars(year),cols=vars(site))+geom_point()+geom_line()+
  geom_errorbar(aes(ymin=site_avg_poll-se_avg_poll,
                    ymax=site_avg_poll+se_avg_poll),width=0.2)+
  labs(title="SH3814LL",y="Avg # Pollinators ± SE")  

```
Note: angry model
```{r echo=TRUE}
SH_poll_mod<-lmer(count~year*sampling_round*seed_coat+(1|site/variety_name),
                    data=SH_insects %>% filter(functional_group=="pollinator"))

# anova(SH_poll_mod)
# summary(SH_poll_mod)
# plot(SH_poll_mod)
# hist(residuals(SH_poll_mod))
```


## Plant Biomass
```{r echo=FALSE}
# subset data for analysis
SH_biomass<-biomass %>%
  filter(brandline=="SH3814 LL")

# summary table for graphs
SH_biomass_siteAvgDf<-biomass %>%
  filter(brandline=="SH3814 LL") %>%
  group_by(site,year,brandline,seed_treat) %>%
  summarise(site_avg_plant_biomass=mean(plant_biomass_g,na.rm=T),
            se_plant_biomass=sd(plant_biomass_g,na.rm = T)/sqrt(n()),
            site_avg_beans=mean(beans_g,na.rm=T),
            se_beans=sd(beans_g,na.rm = T)/sqrt(n()),
            site_avg_yield=mean(plot_yield_buac,na.rm=T),
            se_yield=sd(plot_yield_buac,na.rm = T)/sqrt(n()))

# plant biomass panels
ggplot(SH_biomass_siteAvgDf,aes(x=site,y=site_avg_plant_biomass,group=seed_treat,color=seed_treat))+
         geom_line(size=1.5)+
         geom_point()+
         geom_errorbar(aes(ymin=site_avg_plant_biomass-se_plant_biomass,
                           ymax=site_avg_plant_biomass+se_plant_biomass),width=0.2,size=1.5)+
         facet_wrap(~year,nrow=1)+
  labs(title="SH3814 LL",y="Avg Whole Plant Biomass (g) +/- SE")
```

```{r echo=TRUE}
SH_biomass_mod<-lmer(plant_biomass_g~year*seed_treat+(1|site/brandline),data=SH_biomass)

anova(SH_biomass_mod)
summary(SH_biomass_mod)
plot(SH_biomass_mod)
hist(residuals(SH_biomass_mod))
```

## Trial Yield
```{r echo=FALSE}
# trial yield panels
ggplot(SH_biomass_siteAvgDf,aes(x=site,y=site_avg_yield,group=seed_treat,color=seed_treat))+
         geom_line(size=1.5)+
         geom_point()+
         geom_errorbar(aes(ymin=site_avg_yield-se_yield,
                           ymax=site_avg_yield+se_yield),width=0.2,size=1.5)+
         facet_wrap(~year,nrow=1)+
  labs(title="SH3814 LL",y="Avg Plot Yield (bu/ac) +/- SE")
```

```{r echo=TRUE}
SH_yield_mod<-lmer(plot_yield_buac~year*seed_treat+(1|site/brandline),data=SH_biomass)

anova(SH_yield_mod)
summary(SH_yield_mod)
plot(SH_yield_mod)
hist(residuals(SH_yield_mod))
```