---
title: "Seedcoat Results"
author: "Kelsey McGurrin"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,include = TRUE,message = FALSE)

#### setup ####
#packages
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
library(ggpubr)
library(tidylog)
library(DHARMa)


#### import damage data ####
damage2019 <- read.csv('C:/Users/kmcgurri/Dropbox/bean_dip_2018-2024/field trials/data/clean_data/clean_damage_2019.csv') %>% 
  mutate(year=2019,
         variety_name=case_when(variety %in% c(67,27) ~ 'AG38X8'),
         seed_coat=case_when(variety==67 ~ 'untrt',
                             variety==27 ~ 'trt')) %>%
  select(year,sampling.round,site,variety_name,seed_coat,plot,row,chew_pct,pct_leaves_stippled,pct_damage_stippled) 
damage2020 <- read.csv('C:/Users/kmcgurri/Dropbox/bean_dip_2018-2024/field trials/data/clean_data/clean_damage_2020.csv') %>% 
  mutate(year=2020,
         variety_name=case_when(variety %in% c(2,5) ~ 'AG38X8'),
         seed_coat=case_when(variety==2 ~ 'untrt',
                             variety==5 ~ 'trt')) %>%
  filter(!is.na(variety_name)) %>%
  select(year,sampling.round,site,variety_name,seed_coat,plot,row,chew_pct,pct_leaves_stippled,pct_damage_stippled)

damage2021 <- read.csv('C:/Users/kmcgurri/Dropbox/bean_dip_2018-2024/field trials/data/clean_data/clean_damage_2021.csv') %>% 
  mutate(year=2021,
         variety_name=case_when(variety %in% c(19,59) ~ 'AG38X8'),
         seed_coat=case_when(variety == 19 ~ 'untrt',
                             variety == 59 ~ 'trt')) %>%
  filter(!is.na(variety_name)) %>%
  select(year,sampling.round,site,variety_name,seed_coat,plot,row,chew_pct,pct_leaves_stippled,pct_damage_stippled)


damage <- rbind(damage2019, damage2020, damage2021) %>% #bind all data together
  mutate(stip_pct=(pct_leaves_stippled*as.numeric(pct_damage_stippled))/100,.after=chew_pct,.keep="unused") %>% #calculate stippling
  group_by(year, sampling.round, site, variety_name, seed_coat, plot) %>% # average rows a and b to get one value per plot
  summarise(across(chew_pct:stip_pct, ~ mean(.x, na.rm = TRUE))) %>%
  ungroup()

# df = 1 row per plot
damage |> filter(year==2021)
# should have 1 variety * 2 coats * 4 sites * 3 plots * 4 rounds = 96 rows for 2019 (yes)
# should have 1 variety * 2 coats * 4 sites * 3 plots * 5 rounds = 120 rows for 2020 (yes)
# should have 1 variety * 2 coats * 4 sites * 3 plots * 4 rounds = 96 rows for 2021 (yes)

# so sites display properly from west to east
damage$site<-factor(damage$site, levels = c("K", "C", "W", "PH"))

# add in weeks after planting info
damage<-damage %>% mutate(weeks_ap=case_when((year==2019 & sampling.round==1) ~ 3,
                                   (year==2019 & sampling.round==2) ~ 6,
                                   (year==2019 & sampling.round==3) ~ 9,
                                   (year==2019 & sampling.round==4) ~ 13,
                                   (year==2020 & sampling.round==1) ~ 3,
                                   (year==2020 & sampling.round==2) ~ 6,
                                   (year==2020 & sampling.round==3) ~ 9,
                                   (year==2020 & sampling.round==4) ~ 12,
                                   (year==2020 & sampling.round==5) ~ 15,
                                   (year==2021 & sampling.round==1) ~ 4,
                                   (year==2021 & sampling.round==2) ~ 7,
                                   (year==2021 & sampling.round==3) ~ 9,
                                   (year==2021 & sampling.round==4) ~ 15
                                   ))

#### import biomass data ####

# open clean data file 
# filter so only varieties/years where we have a treated/untreated comparison
biomass<-read_csv("C:/Users/kmcgurri/Dropbox/bean_dip_2018-2024/field trials/data/clean_data/clean_all_years_long.csv") 

biomass<- biomass %>%
  filter(brandline=="AG38X8") %>%
  filter(year %in% c(2019,2020,2021)) %>%
  select(year:row,plant_biomass_g,beans_g) %>%
  unique() # 2019 PH 27-2-4 had two photosynq measurements, leading to duplicate in joined df. drop artifact.


# df= 1 row per plant
biomass |> filter(year==2021)
# should have (6 reps AG38X8 untreated + 4 reps AG38X8 treated) * 4 sites * 3 plots = 120 rows for 2019 (yes)
# should have (6 reps AG38X8 untreated + 4 reps AG38X8 treated) * 4 sites * 3 plots = 120 rows for 2020 (119)
# should have (6 reps AG38X8 untreated + 4 reps AG38X8 treated) * 4 sites * 3 plots = 120 rows for 2021 (yes)

# so sites display properly from west to east
biomass$site<-factor(biomass$site, levels = c("K", "C", "W", "PH"))

```



# Chewing Damage

## 2019
```{r echo=TRUE}
ggplot(data=filter(damage,year==2019),aes(x=chew_pct))+geom_histogram(binwidth = 1)
chew_2019_mod<-lmer(chew_pct~seed_coat*as.factor(sampling.round)+(1|site),data=filter(damage,year==2019))
anova(chew_2019_mod)
summary(chew_2019_mod)
simulationOutput<-simulateResiduals(fittedModel = chew_2019_mod)
plot(simulationOutput)
emmeans(chew_2019_mod,specs = pairwise ~ sampling.round) 
```
round 4 higher than others

## 2020
```{r echo=TRUE}
ggplot(data=filter(damage,year==2020),aes(x=chew_pct))+geom_histogram(binwidth = 1)
chew_2020_mod<-lmer(chew_pct~seed_coat*as.factor(sampling.round)+(1|site),data=filter(damage,year==2020))
anova(chew_2020_mod)
summary(chew_2020_mod)
simulationOutput<-simulateResiduals(fittedModel = chew_2020_mod)
plot(simulationOutput)
emmeans(chew_2020_mod,specs = pairwise ~ sampling.round) 
```
round 1 lower than others; 2 lower than 3, 4, 5; 5 higher than 3 or 4

## 2021 
```{r echo=TRUE} 
ggplot(data=filter(damage,year==2021),aes(x=chew_pct))+geom_histogram(binwidth = 1)
chew_2021_mod<-lmer(chew_pct~seed_coat*as.factor(sampling.round)+(1|site),data=filter(damage,year==2021))
anova(chew_2021_mod)
summary(chew_2021_mod)
simulationOutput<-simulateResiduals(fittedModel = chew_2021_mod)
plot(simulationOutput)
emmeans(chew_2021_mod,specs = pairwise ~ sampling.round) 
```
round 1 higher than 2 or 3



# Stippling Damage

## 2019
```{r echo=TRUE}
ggplot(data=filter(damage,year==2019),aes(x=stip_pct))+geom_histogram(binwidth = 1)
stip_2019_mod<-lmer(stip_pct~seed_coat*as.factor(sampling.round)+(1|site),data=filter(damage,year==2019))
anova(stip_2019_mod)
summary(stip_2019_mod)
simulationOutput<-simulateResiduals(fittedModel = stip_2019_mod)
plot(simulationOutput)
emmeans(stip_2019_mod,specs = pairwise ~ seed_coat | sampling.round) 
```
round 1: untreated higher

## 2020
```{r echo=TRUE}
ggplot(data=filter(damage,year==2020),aes(x=stip_pct))+geom_histogram(binwidth = 1)
# stip_2020_mod<-lmer(stip_pct~seed_coat*as.factor(sampling.round)+(1|site),data=filter(damage,year==2020))
# anova(stip_2020_mod)
# summary(stip_2020_mod)
# simulationOutput<-simulateResiduals(fittedModel = stip_2020_mod)
# plot(simulationOutput)
# emmeans(stip_2020_mod,specs = pairwise ~ sampling.round) 
# # residuals bad
# # round 5 higher than others

# try sqrt transforming
stip_2020_mod2<-lmer(log(stip_pct+1)~seed_coat*as.factor(sampling.round)+(1|site),data=filter(damage,year==2020))
anova(stip_2020_mod2)
simulationOutput<-simulateResiduals(fittedModel = stip_2020_mod2)
plot(simulationOutput)
emmeans(stip_2020_mod2,specs = pairwise ~ sampling.round) 
```
round 1,2,3 lower than 4 or 5; 4 lower than 5


## 2021 
```{r echo=TRUE}
ggplot(data=filter(damage,year==2021),aes(x=stip_pct))+geom_histogram(binwidth = 1)
# stip_2021_mod<-lmer(stip_pct~seed_coat*as.factor(sampling.round)+(1|site),data=filter(damage,year==2021)) 
# anova(stip_2021_mod)
# summary(stip_2021_mod)
# simulationOutput<-simulateResiduals(fittedModel = stip_2021_mod)
# plot(simulationOutput)
# emmeans(stip_2021_mod,specs = pairwise ~ seed_coat | sampling.round)
# # residuals bad
# # round 4: treated higher

# try sqrt transforming
stip_2021_mod2<-lmer(log(stip_pct+1)~seed_coat*as.factor(sampling.round)+(1|site),data=filter(damage,year==2021)) 
anova(stip_2021_mod2)
summary(stip_2021_mod2)
simulationOutput<-simulateResiduals(fittedModel = stip_2021_mod2)
plot(simulationOutput)
emmeans(stip_2021_mod2,specs = pairwise ~ sampling.round)
```
round 4 higher than others



# Combined Damage Figure
```{r echo=FALSE}
# summary table for mean and SE
damage_siteAvgDf<-damage %>%
  group_by(sampling.round,weeks_ap,year,seed_coat) %>%
  summarise(site_avg_chew=mean(chew_pct,na.rm=T),
            se_avg_chew=sd(chew_pct,na.rm = T)/sqrt(n()),
            site_avg_stip=mean(stip_pct,na.rm=T),
            se_avg_stip=sd(stip_pct,na.rm=T)/sqrt(n()))

color_chewing_facet<-
  ggplot(damage_siteAvgDf, aes(x=weeks_ap,y=site_avg_chew,shape=seed_coat,color=seed_coat,group=seed_coat,
                               linetype = seed_coat))+geom_line()+facet_wrap(~year)+geom_point(size=2)+
  geom_errorbar(aes(ymin=site_avg_chew-se_avg_chew,
                      ymax=site_avg_chew+se_avg_chew),width=0.2)+
  scale_shape_manual(values = c(17,19),labels=c("Treated","Untreated"))+
  scale_color_manual(values=c("#f1a340","#998ec3"),labels=c("Treated","Untreated"))+
  scale_linetype_manual(values=c("solid","dashed"),labels=c("Treated","Untreated"))+
  labs(y="Chewing Damage\nAvg % ± SE",x="",
         shape="Seed Coat",color="Seed Coat",linetype="Seed Coat") + 
    theme_bw() + theme(panel.grid.minor = element_blank(),
                     strip.text = element_text(face="bold"),
                     plot.margin = unit(c(0,0,0,0), 'lines'))+scale_x_continuous(breaks=c(3,6,9,12,15))

color_stippling_facet<-
  ggplot(damage_siteAvgDf, aes(x=weeks_ap,y=site_avg_stip,shape=seed_coat,color=seed_coat,group=seed_coat,
                               linetype = seed_coat))+geom_line()+facet_wrap(~year)+geom_point(size=2)+
  geom_errorbar(aes(ymin=site_avg_stip-se_avg_stip,
                      ymax=site_avg_stip+se_avg_stip),width=0.2)+
  scale_shape_manual(values = c(17,19),labels=c("Treated","Untreated"))+
  scale_color_manual(values=c("#f1a340","#998ec3"),labels=c("Treated","Untreated"))+
  scale_linetype_manual(values=c("solid","dashed"),labels=c("Treated","Untreated"))+
  labs(y="Stippling Damage\nAvg % ± SE",x="Weeks After Planting",
         shape="Seed Coat",color="Seed Coat",linetype="Seed Coat") + 
    theme_bw() + theme(panel.grid.minor = element_blank(),
                     strip.text = element_text(face="bold"),
                     plot.margin = unit(c(0,0,0,0), 'lines'))+scale_x_continuous(breaks=c(3,6,9,12,15))+
  geom_text(data = filter(damage_siteAvgDf,year==2019),aes(x = 3.5, y = 5,label = "**"),color="black",size=10)

color_damage_figure <- ggarrange(color_chewing_facet, color_stippling_facet, 
                    labels = c("A", "B"),
                    ncol = 1, nrow = 2,common.legend = TRUE, legend = "bottom",hjust=-1,vjust=1,align = c("v"))

#ggsave("C:\\Users\\kmcgurri\\Dropbox\\bean_dip_2018-2024\\manuscripts\\field trial seed coats\\figures\\color_damage_figure.tiff",plot=color_damage_figure,width=6,height=4,units=c("in"))

```



# Plant Biomass

## 2019
```{r echo=TRUE}
ggplot(data=filter(biomass,year==2019),aes(x=plant_biomass_g))+geom_histogram(binwidth = 1)
biomass_2019_mod<-lmer(plant_biomass_g~seed_treat+(1|site),data=filter(biomass,year==2019))
anova(biomass_2019_mod)
summary(biomass_2019_mod)
simulationOutput<-simulateResiduals(fittedModel = biomass_2019_mod)
plot(simulationOutput)
emmeans(biomass_2019_mod,specs = pairwise ~ seed_treat) 
```
untreated is higher

## 2020
```{r echo=TRUE}
# ggplot(data=filter(biomass,year==2020),aes(x=plant_biomass_g))+geom_histogram(binwidth = 1)
# biomass_2020_mod<-lmer(plant_biomass_g~seed_treat+(1|site),data=filter(biomass,year==2020))
# anova(biomass_2020_mod)
# summary(biomass_2020_mod)
# simulationOutput<-simulateResiduals(fittedModel = biomass_2020_mod)
# plot(simulationOutput)
# # residuals bad

# try sqrt transforming
biomass_2020_mod2<-lmer(log(plant_biomass_g+1)~seed_treat+(1|site),data=filter(biomass,year==2020))
anova(biomass_2020_mod2)
summary(biomass_2020_mod2)
simulationOutput<-simulateResiduals(fittedModel = biomass_2020_mod2)
plot(simulationOutput)
```


## 2021 
```{r echo=TRUE}
ggplot(data=filter(biomass,year==2021),aes(x=plant_biomass_g))+geom_histogram(binwidth = 1)
biomass_2021_mod<-lmer(plant_biomass_g~seed_treat+(1|site),data=filter(biomass,year==2021))
anova(biomass_2021_mod)
summary(biomass_2021_mod)
simulationOutput<-simulateResiduals(fittedModel = biomass_2021_mod)
plot(simulationOutput)
```



# Beans per Plant

## 2019
```{r echo=TRUE}
ggplot(data=filter(biomass,year==2019),aes(x=beans_g))+geom_histogram(binwidth = 1)
beans_2019_mod<-lmer(beans_g~seed_treat+(1|site),data=filter(biomass,year==2019))
anova(beans_2019_mod)
summary(beans_2019_mod)
simulationOutput<-simulateResiduals(fittedModel = beans_2019_mod)
plot(simulationOutput)
emmeans(beans_2019_mod,specs = pairwise ~ seed_treat) 
```
untreated is higher

## 2020
```{r echo=TRUE}
ggplot(data=filter(biomass,year==2020),aes(x=beans_g))+geom_histogram(binwidth = 1)
beans_2020_mod<-lmer(beans_g~seed_treat+(1|site),data=filter(biomass,year==2020))
anova(beans_2020_mod)
summary(beans_2020_mod)
simulationOutput<-simulateResiduals(fittedModel = beans_2020_mod)
plot(simulationOutput)
```

## 2021 
```{r echo=TRUE}
ggplot(data=filter(biomass,year==2021),aes(x=plant_biomass_g))+geom_histogram(binwidth = 1)
beans_2021_mod<-lmer(beans_g~seed_treat+(1|site),data=filter(biomass,year==2021))
anova(beans_2021_mod)
summary(beans_2021_mod)
simulationOutput<-simulateResiduals(fittedModel = beans_2021_mod)
plot(simulationOutput)
```



# Combined Harvest Figure
```{r echo=FALSE}
# summary table for mean and SE
biomass_siteAvgDf<-biomass %>%
  group_by(year,seed_treat) %>%
  summarise(site_avg_plant_biomass=mean(plant_biomass_g,na.rm=T),
            se_plant_biomass=sd(plant_biomass_g,na.rm = T)/sqrt(n()),
            site_avg_beans=mean(beans_g,na.rm=T),
            se_beans=sd(beans_g,na.rm = T)/sqrt(n()))

color_biomass_facet<-
  ggplot(biomass_siteAvgDf,aes(x=rev(seed_treat),y=site_avg_plant_biomass,
                               shape=rev(seed_treat),linetype=rev(seed_treat),color=rev(seed_treat)))+
         geom_line()+ geom_point(size=3)+ facet_wrap(~year,nrow=1)+
  scale_linetype_manual(values=c("dashed","solid"),labels=c("Untreated","Treated"))+
  scale_shape_manual(values = c(19,17),labels=c("Untreated","Treated"))+
  scale_color_manual(values=c("#998ec3","#f1a340"),labels=c("Untreated","Treated"))+
         geom_errorbar(aes(ymin=site_avg_plant_biomass-se_plant_biomass,
                           ymax=site_avg_plant_biomass+se_plant_biomass),width=0.2)+
         
  labs(y="Whole Biomass (g)\nAvg ± SE",x="")+
  scale_x_discrete(labels=c("Untreated","Treated")) +
  scale_y_continuous(limits = c(27,52))+
  theme_bw() + theme(panel.grid.minor = element_blank(),
                     strip.text = element_text(face="bold",size=rel(1.5)),legend.position = "none")+
  geom_text(data = filter(biomass_siteAvgDf,year==2019),aes(x = 1.5, y = 45,label = "*"),color="black",size=10)

color_beans_facet<-
  ggplot(biomass_siteAvgDf,aes(x=rev(seed_treat),y=site_avg_beans,
                               shape=rev(seed_treat),linetype=rev(seed_treat),color=rev(seed_treat)))+
         geom_line()+ geom_point(size=3)+ facet_wrap(~year,nrow=1)+
  scale_linetype_manual(values=c("dashed","solid"),labels=c("Untreated","Treated"))+
  scale_shape_manual(values = c(19,17),labels=c("Untreated","Treated"))+
  scale_color_manual(values=c("#998ec3","#f1a340"),labels=c("Untreated","Treated"))+
         geom_errorbar(aes(ymin=site_avg_beans-se_beans,
                           ymax=site_avg_beans+se_beans),width=0.2)+
  labs(y="Beans per Plant (g)\nAvg ± SE",x="Seed Coat")+
  scale_x_discrete(labels=c("Untreated","Treated")) +
  scale_y_continuous(limits = c(9,27))+
  theme_bw() + theme(panel.grid.minor = element_blank(),
                     strip.text = element_text(face="bold",size=rel(1.5)),legend.position = "none")+
  geom_text(data = filter(biomass_siteAvgDf,year==2019),aes(x = 1.5, y = 19,label = "*"),color="black",size=10)

color_harvest_figure <- ggarrange(color_biomass_facet, color_beans_facet, 
                    labels = c("A", "B"),
                    ncol = 1, nrow = 2, legend = "none",hjust=-1,vjust=1,align = c("v"))

#ggsave("C:\\Users\\kmcgurri\\Dropbox\\bean_dip_2018-2024\\manuscripts\\field trial seed coats\\figures\\color_harvest_figure.tiff",plot=color_harvest_figure,width=6,height=4,units=c("in"))

```



# Other Facts for pub

## Most common insects
```{r echo=FALSE}
bugs19 <- read.csv('C:/Users/kmcgurri/Dropbox/bean_dip_2018-2024/field trials/data/clean_data/clean_damage_2019.csv') %>%
  filter(variety %in% c(67,27)) %>%
  select(insect.names) %>%
  separate_longer_delim(insect.names, delim = ",") %>%
  drop_na() %>%
  mutate(trimmed=str_trim(insect.names,side="left"),.keep="unused") %>%
  separate_wider_regex(trimmed, c(count = ".*?", " ", bugs = ".*")) %>%
  mutate(simple.bugs=case_when(
    str_detect(bugs, "hopper")==T ~ "planthopper",
    str_detect(bugs, "stink")==T ~ "stinkbug",
    str_detect(bugs, "thrip")==T ~ "thrips",
    str_detect(bugs, "aphid")==T ~ "aphid",
    str_detect(bugs, "miner")==T ~ "caterpillar",
    str_detect(bugs, "clover")==T ~ "caterpillar",
    str_detect(bugs, "duskywing")==T ~ "caterpillar",
    str_detect(bugs, "fold")==T ~ "caterpillar",
    str_detect(bugs, "caterpillar")==T ~ "caterpillar",
    str_detect(bugs, "morbia")==T ~ "caterpillar",
    str_detect(bugs, "geo")==T ~ "caterpillar",
    str_detect(bugs, "roll")==T ~ "caterpillar",
    str_detect(bugs, "cocoon")==T ~ "caterpillar",
    str_detect(bugs, "rctiid")==T ~ "caterpillar",
    str_detect(bugs, "bug")==T ~ "bug",
    str_detect(bugs, "beetle")==T ~ "beetle",
  )) 

bugs20 <- read.csv('C:/Users/kmcgurri/Dropbox/bean_dip_2018-2024/field trials/data/clean_data/clean_damage_2020.csv') %>%
  filter(variety %in% c(2,5)) %>%
  select(insect.names) %>%
  separate_longer_delim(insect.names, delim = ",") %>%
  drop_na() %>%
  mutate(trimmed=str_trim(insect.names,side="left"),.keep="unused") %>%
  separate_wider_regex(trimmed, c(count = ".*?", " ", bugs = ".*"),too_few = "align_start") %>%
  mutate(simple.bugs=case_when(
    str_detect(bugs, "hopper")==T ~ "planthopper",
    str_detect(bugs, "stink")==T ~ "stinkbug",
    str_detect(bugs, "thrip")==T ~ "thrips",
    str_detect(bugs, "aphid")==T ~ "aphid",
    str_detect(bugs, "miner")==T ~ "caterpillar",
    str_detect(bugs, "clover")==T ~ "caterpillar",
    str_detect(bugs, "duskywing")==T ~ "caterpillar",
    str_detect(bugs, "skipper")==T ~ "caterpillar",
    str_detect(bugs, "fold")==T ~ "caterpillar",
    str_detect(bugs, "caterpillar")==T ~ "caterpillar",
    str_detect(bugs, "morbia")==T ~ "caterpillar",
    str_detect(bugs, "geo")==T ~ "caterpillar",
    str_detect(bugs, "roll")==T ~ "caterpillar",
    str_detect(bugs, "cocoon")==T ~ "caterpillar",
    str_detect(bugs, "rctiid")==T ~ "caterpillar",
    str_detect(bugs, "looper")==T ~ "caterpillar",
    str_detect(bugs, "bug")==T ~ "bug",
    str_detect(bugs, "beetle")==T ~ "beetle",
  )) 

bugs21 <- read.csv('C:/Users/kmcgurri/Dropbox/bean_dip_2018-2024/field trials/data/clean_data/clean_damage_2021.csv') %>%
  filter(variety %in% c(19,59,57,58)) %>%
  select(insect.names) %>%
  separate_longer_delim(insect.names, delim = ",") %>%
  drop_na() %>%
  mutate(trimmed=str_trim(insect.names,side="left"),.keep="unused") %>%
  separate_wider_regex(trimmed, c(count = ".*?", " ", bugs = ".*"),too_few = "align_start") %>%
  mutate(simple.bugs=case_when(
    str_detect(bugs, "hopper")==T ~ "planthopper",
    str_detect(bugs, "PLH")==T ~ "planthopper",
    str_detect(bugs, "thrip")==T ~ "thrips",
    str_detect(bugs, "stink")==T ~ "stinkbug",
    str_detect(bugs, "aphid")==T ~ "aphid",
    str_detect(bugs, "miner")==T ~ "caterpillar",
    str_detect(bugs, "clover")==T ~ "caterpillar",
    str_detect(bugs, "duskywing")==T ~ "caterpillar",
    str_detect(bugs, "skipper")==T ~ "caterpillar",
    str_detect(bugs, "fold")==T ~ "caterpillar",
    str_detect(bugs, "caterpillar")==T ~ "caterpillar",
    str_detect(bugs, "morbia")==T ~ "caterpillar",
    str_detect(bugs, "geo")==T ~ "caterpillar",
    str_detect(bugs, "roll")==T ~ "caterpillar",
    str_detect(bugs, "cocoon")==T ~ "caterpillar",
    str_detect(bugs, "rctiid")==T ~ "caterpillar",
    str_detect(bugs, "looper")==T ~ "caterpillar",
    str_detect(bugs, "tier")==T ~ "caterpillar",
    str_detect(bugs, "bug")==T ~ "bug",
    str_detect(bugs, "beetle")==T ~ "beetle",
  )) 

rbind(bugs19,bugs20,bugs21)%>%
  group_by(simple.bugs) %>%
  summarize(total=sum(as.numeric(count),na.rm = T)) %>%
  arrange(desc(total)) %>%
  drop_na() # NAs are pollinators, predators, borers, unknowns
```

## Percent change for harvest metrics
(final-initial)/initial
```{r}
# whole plant biomass 
biomass_siteAvgDf %>% filter(year==2019) %>% 
  summarize(((site_avg_plant_biomass[seed_treat=="treated"]-site_avg_plant_biomass[seed_treat=="untreated"])/
              site_avg_plant_biomass[seed_treat=="untreated"])*100
            )

# bean yield 
biomass_siteAvgDf %>% filter(year==2019) %>% 
  summarize(((site_avg_beans[seed_treat=="treated"]-site_avg_beans[seed_treat=="untreated"])/
              site_avg_beans[seed_treat=="untreated"])*100
            )

```


# Session Info
```{r echo=FALSE}
sessionInfo()
```

# Alternative analysis methods
## All years together
### Chewing
```{r echo=TRUE}
ggplot(data=damage,aes(x=chew_pct))+geom_histogram(binwidth = 1)
chew_mod<-lmer(chew_pct~seed_coat*as.factor(sampling.round)*as.factor(year)+(1|site),data=damage)
anova(chew_mod)
summary(chew_mod)
simulationOutput<-simulateResiduals(fittedModel = chew_mod)
plot(simulationOutput)
emmeans(chew_mod,specs = pairwise ~ seed_coat | sampling.round | year)
```
no diffs

### Stippling
```{r}
ggplot(data=damage,aes(x=stip_pct))+geom_histogram(binwidth = 1)
stip_mod<-lmer(stip_pct~seed_coat*as.factor(sampling.round)*as.factor(year)+(1|site),data=damage)
anova(stip_mod)
summary(stip_mod)
simulationOutput<-simulateResiduals(fittedModel = stip_mod)
plot(simulationOutput)
emmeans(stip_mod,specs = pairwise ~ seed_coat | sampling.round | year)
```
residuals bad
2019 round 1 and 2021 round 4 treat diffs- same as main analysis

### Biomass
```{r}
ggplot(data=biomass,aes(x=plant_biomass_g))+geom_histogram(binwidth = 1)
biomass_mod<-lmer(plant_biomass_g~seed_treat*as.factor(year)+(1|site),data=biomass)
anova(biomass_mod)
summary(biomass_mod)
simulationOutput<-simulateResiduals(fittedModel = biomass_mod)
plot(simulationOutput)
emmeans(biomass_mod,specs = pairwise ~ seed_treat | year) 
```
residuals bad
no diffs

### Beans
```{r}
ggplot(data=biomass,aes(x=beans_g))+geom_histogram(binwidth = 1)
beans_mod<-lmer(beans_g~seed_treat*as.factor(year)+(1|site),data=biomass)
anova(beans_mod)
summary(beans_mod)
simulationOutput<-simulateResiduals(fittedModel = beans_mod)
plot(simulationOutput)
emmeans(beans_mod,specs = pairwise ~ seed_treat | year) 
```
no diffs
